---
title: "CQ 2019 election results"
author: 
date: 
output:
  xaringan::moon_reader:
    css: ["default", "libs/mjc-css/mjc-theme.css", "libs/mjc-css/mjc-fonts.css"]
    lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, dpi = 300, fig.height = 5)

library(knitr)

source("sa_map.R")
source("C:/Users/matt/Documents/R/election_2019_nd/election_2019.R")
```

# CQ analysis of 2019 election 

- These slides provide some detailed information of the results of the federal election in 2019 in Central Queenslans. 

- Online versions of the maps can be found at https://mattjcan.github.io/sa_map/....html

---

# We did well in coal seats

``` {r }
grid.arrange(p_tpp_coal, p_tpp_coal_swing, ncol = 1)
```

---

# The LNP did well across CQ

``` {r }
grid.arrange(p_tpp_coal_div, p_tpp_coal_div_swing, ncol = 1)
```

---
  
# Statistically true too! 

``` {r }
grid.arrange(p_min_swing, p_lm_coal, ncol = 1)
```

---

# The Labor vote collapsed in coal seats 

``` {r }
grid.arrange(p_pd_coal_alp, p_pd_coal_alp_swing, ncol = 1)
```

---

# TPP swing

```{r }
frameWidget(m_sa1_s_cq, width='100%', height = '500px')
```

---

# TPP swing

```{r }
frameWidget(m_sa2_s_cq, width='100%', height = '500px')
```

---

# TPP

```{r }
frameWidget(m_sa1_cq, width='100%', height = '500px')
```

---

# TPP 

```{r }
frameWidget(m_sa2_cq, width='100%', height = '500px')
```

---

# Preference flows

``` {r }
p_dop_cq
```

---

# CQ state seats 

```{r }
frameWidget(m_cq_state, width='100%', height = '500px')
```

---


# Central Queensland state seats

``` {r }
p_tpp_state_cq
```

---

# Central Queensland state seats

``` {r }
grid.arrange(p_p_state$Mirani, p_p_state$Keppel, p_p_state$Rockhampton, p_p_state$Gladstone, ncol = 2) 
```

---

# Central Queensland state seats

``` {r }
grid.arrange(p_p_state$Gregory, p_p_state$Callide, p_p_state$Burnett, p_p_state$Nanango, ncol = 2) 
```